|

### 2025-01-31 doc/paper.qmd
comm

>>>>

```{python}
#| label: fig-abnormal-r2
#| fig-cap: "Replicated Figure 1: Abnormal Adjusted R² Values and Slope Coefficients from Annual Regressions"
#| fig-align: center
#| echo: false

import pickle
import matplotlib.pyplot as plt

# Load the figure from the pickle file
with open('../output/figure1_replication.pickle', 'rb') as f:
    fig = pickle.load(f)

# Render the figure explicitly
plt.figure(fig.number)
plt.show()
```
